Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-06-23 paper.tex
Fixed data collection methods

		\subsection{Considerations about the survey}

			\noindent The two presented methods proposed for data collection are very different. Both of these have their own peculiarities. The first method can help in having a typicality value for every image collected in the dataset, 
			while the alternative does not. Given the large number of images that should be used, though, it is not feasible to ask the subjects to rate the typicality value of all the images of the dataset. In fact, it is very likely 
			that a subject that has to rate the typicality of a large number of images will be tired after a certain number of images, polluting the results of the survey. A possible solution to this problem is to 
			divide the survey so that subjects have to rate the typicality of a limited number of images. This method would result in a lower amount of data, but at the same time, a more precise amount of data. Another 
			problem with this method it is that it has a possible bias. In fact, if a person sees a bird, for example a swan, or a duck, and is asked to rate its typicality, most likely will rate it in the higher part 
			of the scale, while if asked to list a certain number of birds it is more likely that it is not present than that it is present.\\
			On the other hand, the second method gives a possibly lower bias, since there are no images that can influence the subject's mind showing images of examples of the category that the subject did not think of. 
			Recalling the previous example with the swan, if a person does not think of the swan, it would not be present in the list created by the subject. This could result in a lower bias, but it comes at the cost 
			of having to interview more people and, most likely, not having enough data for some of the examples. In this approach, the more a bird is typical, the more it appears in the lists and in higher positions. 
			There is an example in the appendix. Even though this method has the advantage of having less bias, has a  great drawback. That is, in particular, the fact that the prototype construction is very difficult.\\
			In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two 
			methods have the right weight and it is easier to decide which one is more convenient.
			As alternative, it is possible to try both the methods and see which one gives better results. In this way, both the possibilities will be used and there is the possibility to see which one is better in 
			terms of performance.

>>>>

		\subsection{Considerations about the survey\lable{sec:cas}}

			\subsubsection{Considerations}
				\noindent The first two presented methods have a quite similar concept behind them. Although it is still a matter of discussion which one is more reliable, especially in children, as seen in \cite{maridaki1997rating} 
				and \cite{10.1371/journal.pone.0157936}, both these methods have been used to collect typicality informations. The main difference in these two methods is that the first one, which is based on 
				ratings, the researchers may have biased data since it is possible that seeing a picture of an example of the category the subject can be biased. On the other hand, the other method does not present 
				this kind of bias, but presents a higher difficulty on in extracting the typicality values. \\
				The alternative possible proposed method, can show a lower bias than the bias of the rating method since no images influence the subject's ratings. Moreover, it is easier to infer a typicality value 
				than in the ranking method, since a higher position on the list corresponds to a higher typicality. 
				Another positive aspect of this method is that if a person did not think of a particular example, it won't appear on the ratings. This fact can help identifying the real typicality 
				without the possible bias introduced by presenting to a subject an image of an example that did not come to mind.

			\subsubsection{Limitations and negative aspects}

				The biggest problematic related to the first two methods presented, which are the rating and the ranking systems, is that it is not feasible to either rate or rank every example in the whole 
				dataset, since it must have many images. In fact, it is very likely that a subject that has to rate or rank many examples will be tired after a certain number of images, polluting the results of the survey.
				The possible solution to this problem, is to give the subjects a subset of images to rate or rank. In this way, the collected data are most likely more reliable than the ones collected on all the dataset, 
				so it is more accurate the final result. \\
				Regarding only the typicality rating system, there is another problem. As hinted in previously, there is the possibility that this procedure leads to biased data. That is true because the form 
				created to collect the data, presents an example of an object that the subjects may not have thought of, and presenting the image, it may be possible that the subject gives a biased answer since 
				the image could have influenced the subject's judgement. For example, let us assume that the category chosen for the experiments is ``bird''. If a person is presented and image of a swan, 
				or a duck, and is asked to rate its typicality, most likely will rate it in the higher part of the scale, while if asked to list a certain number of birds it is more likely that it is not 
				present than that it is present.\\
				Talking about the ranking system, also this method can present biased data, since also this method presents the images, even if the bias is probably lower than the one that could result with the ranking system. 
				The major problem, with this method, is that the researcher must also design an algorithm to infer the typicality values from the rankings. This is a very difficult algorithm to design, since the rankings must 
				find a mapping to a scale.\\
				The alternative possibility described, can result in a lower bias since no images influence the subject's judgments. Recalling the previous example, in fact, if the subject did not think of 
				ducks and swans in the category ``bird'', these examples will not appear on the list. Although this technique presents a lower bias, it results in a great difficulty in prototype construction.

			\subsubsection{Considerations on how to choose}
				In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two 
				methods have the right weight and it is easier to decide which one is more convenient.
				As alternative, it is possible to try both the methods and see which one gives better results. In this way, both the possibilities will be used and there is the possibility to see which one is better in 
				terms of performance.
